---
title: "Fantasy Football"
author: "Andrew Little"
date: "25/01/2021"
output:
  pdf_document: default
  html_document: default
---

# As a markov chain -------------------------------------------------------

At each gameweek, we have 11 players that will play. Let's assume
that these are the only players we have control of (i.e. no subs).

There are N total players on the game (N~650), and given some conditions, are available to be bought.

We will start assuming that we must make one transfer or less each gameweek, unlike in
Fantasy football where you can pay 4 points to do an extra.

On gameweek one, the state of our team is:

* $\underline{s_1} = \{s_{1j}\}_{j=1}^{j=11}$

i.e. $\underline{s_1}$ is an eleven-vector

Here, we let $s_{ij}$ represent the player in the $j^{th}$ player slot on gameweek $i$.


Let's fix $\underline{s_1}$:

$$\underline{s_1} \equiv \{s_{1_{1}}, s_{1_{2}}, ..., s_{1_{{11}}}\} \in \{1, 2, ..., N\}^{11}$$
- Note that we cannot select a single player more than once, and so we have for fixed $i$:

  * $\forall (j, k) \in \{1, 2, ..., 11\}^2$, $s_{i_j} \neq{} s_{i_k}$ for $j \neq k$.
  

For gameweek 2, we can now transition to another state. Essentially, we have the following two choices:

- We could swap out one $s_{1_j} \in \{1, 2, ..., N\}$ for $s_{2_j}$.
- We could make no transfers so that $\underline{s_1} = \underline{s_2}$

- We have $11(N-11)$ ~  $7029$ choices for transfer as we can swap any of the 11 players out, and for each player that we swap out, we have $N-11$ choices, as we cannnot swap for the same people.

We must filter out:
- The players that are out of pay range, given who they are substituted for.
- Therefore we will need to apply the filter for each player, and then bind the tables together.


## Finding the possible transfers

We will first give a toy example, assuming we are in gameweek one. To do this we will use the {fplr} package.

First we give ourselves a random team of 11 to begin with.

```{r}
library(dplyr)
library(fplr)
# Create a dataframe of players and teams simple information
team_lookup <- fpl_get_teams() %>% select(name, id)

player_lookup <- fpl_get_player_all() %>% 
  left_join(team_lookup, c("team" = "id")) %>% 
  select(-team) %>% 
  rename("team_name" = name) %>% 
  select(first_name, second_name, team_name, id)  
```


```{r}
set.seed(1871)
s_1 <- fpl_get_player_all() %>% 
  sample_n(11, replace = FALSE) %>% 
  left_join(team_lookup, c("team" = "id")) %>% 
  select(-team) %>% 
  rename("team_name" = name) %>% 
  select(first_name, second_name, team_name, id, everything())  
s_1
```

Okay so we now have 11 players. Therefore the following transfers are:

```{r}
library(purrr)

# Find players that do not have an id in s1 and then give current id as id_out. Then bind rows.
transfers <- s_1$id %>% 
  map(function(id) {
    transf <- player_lookup %>% 
      rename("id_in" = id) %>% # here id is not the argument to map, but the column in player_lookup
      filter(!(id_in %in% s_1$id)) %>% 
      mutate("id_out" = id)
  }) %>% 
  bind_rows()
transfers
```


Note how we have 642 players to begin with, and thus should expect $11*(642-11)$ total available transfer choices. This is what we have:

```{r}
nrow(transfers)
```

Now let's give a cost to each transfer. Clearly, this is 'player in cost' - 'player out cost':

```{r}
player_costs <- select(fpl_get_player_all(), id, now_cost)

transfers <- transfers %>% 
  left_join(player_costs, 
            by = c("id_in" = "id")) %>% 
  rename("now_cost_in" = now_cost) %>% 
  left_join(player_costs, 
            by = c("id_out" = "id")) %>% 
  rename("now_cost_out" = now_cost) %>% 
  mutate("transfer_cost" = now_cost_in - now_cost_out)
transfers %>% 
  select(transfer_cost, everything())
```



## Assume we already have a model for player's points

We now assume that we have modelled, elsewhere, the expected number of points a player will score in a particular gameweek. Number of points in gameweek $i$ is given by:
  *$p_{i}$


We give this expected number of points as 
